The Jester joke recommender system

### 2021-01-24 inst/jester.Rmd
fixes #72

```{r,label=findmaxp,cache=TRUE}
system.time(mjest <- maxp(jester,n=1))
```

@@

```{r,showmjest}
mjest
plot(mjest)
```

```{r,label=equalptestdoer,cache=TRUE}
equalp.test(jester,startp=indep(mjest))
```

@@

>>>>

```{r,label=findmaxp,cache=TRUE}
system.time(jester_maxp <- maxp(jester,n=1))
```

@@

```{r,showjester_maxp}
jester_maxp
plot(jester_maxp)
```

```{r,label=equalptestdoer,cache=TRUE}
equalp.test(jester,startp=indep(jester_maxp))
```

@@

### Package dataset

Following lines create `jester.rda`, residing in the `data/` directory of the package.

```{r,label=savejesterdataset}
save(jester,jester_maxp,file="jester.rda")
```
